Let us define $V$ to be a {\it logarithmic verifier} for a language $\lang \subseteq \AB^*$ if $V$ is a
deterministic TM with a read-only input-tape, read-once witness-tape and
read-write working-tape such that for every $x \in \AB^*$ it holds that:
\begin{itemize}
    \item $x \in \lang \Longrightarrow \exists w \in \AB^* : V (x, w) = accept$
    \item $x \notin \lang \Longrightarrow \forall w \in \AB^* : V (x, w) = reject$
    \item $V(x, w)$ uses at most $O(log|x|)$ working-tape cells
\end{itemize}
Prove that a language is in $NL$ iff it has a logarithmic verifier.


Proof: \\
We need to show that: \\
1. $\lang \in NL \Rightarrow \lang$ has logarithmic verifier. \\
2. $\lang$ has logarithmic verifier $\Rightarrow \lang \in NL$. \\

\underline{$\lang \in NL \Rightarrow \lang$ has logarithmic verifier:} \\
$\lang \in NL$ so there is non-deterministic TM $N$ that decides it with $O(log(n))$ space complexity.
We shall denote by $b$ the max degree of a vertex in the run tree of $N$ on $x$.
We shall build verifier $V$ for $\lang$. \\
$V$ on input $(x, w)$:
\begin{enumerate}[1., itemsep=5pt]
    \item Until we reach accepting / rejecting configuraion:
    \item \qquad Read $log(b) (=O(1))$ bits of $w$ to decide which configuration branch to take (= deciding which $\de$ move to take).
    \item \qquad Continue simulating the run of $N$ on $x$ using the working tape.
    \item Accept iff we reached an accepting configuration.
\end{enumerate}

The verifier uses the witness as the path to the accepting configuration. \\
So we get $\forall x \in \AB^*$: \\
If $x \in \lang$ \\
$\Longrightarrow$ In one of the computational paths, $N$ will accept $x$ \\
$\Longrightarrow \exists w \in \AB^* : V (x, w) = accept$ \\
If $x \notin \lang$ \\
$\Longrightarrow$ In every computational paths, $N$ will reject $x$ \\
$\Longrightarrow  \forall w \in \AB^* : V (x, w) = reject$ \\

Notice that $V$'s space complexity on input $(x, w)$ (where $|x|=n$) is $O(log(n))$,
since $N$ has logarithmic space complexity. Also, we only read the witness once to know which branch to take.\\
Therefore $\lang$ has logarithmic verifier. \\
Hence $\lang \in NL \Rightarrow \lang$ has a logarithmic verifier. \\

\pagebreak

\underline{$\lang$ has logarithmic verifier $\Rightarrow \lang \in NL$} \\
Let $\lang$ have logarithmic verifier $V$, we shall build non-deterministic TM $N$ for $\lang$. \\
$N$ on input $x$:
\begin{enumerate}[1., itemsep=5pt]
    \item Guess witness $w$ bit by bit and run $V(x,w)$.
    \item Accept iff $V(x,w)$ accepts.
\end{enumerate}

So we get $\forall x \in \AB^*$: \\
If $x \in \lang$ \\
$\Longrightarrow \exists w \in \AB^* : V (x, w) = accept$ \\
$\Longrightarrow$ In one of the computational paths, $N$ will guess the bits of $w$ and $V$ will accept $(x, w)$
(we can guess the witness bit by bit, since $V$ reads the witness only once) \\
$\Longrightarrow N$ accepts

If $x \notin \lang$ \\
$\Longrightarrow \forall w \in \AB^* : V (x, w) = reject$ \\
$\Longrightarrow$ In every computational paths, $V$ will reject $(x, w)$ \\
$\Longrightarrow N$ rejects

Notice that $N$'s space complexity on input $x$ (where $|x|=n$) is $O(log(n))$,
since $V$ is a logarithmic verifier and we always store only $O(1)$ bits of $w$. \\

Therefore $\lang \in NL$. \\
Hence $\lang$ has logarithmic verifier $\Rightarrow \lang \in NL$. \\
In conclusion $\lang \in NL \iff \lang$ has a logarithmic verifier.
