A TM is {\it expected poly-time } if there exists $p \in poly$ such that for every x the
expected running time of $M(x)$ is at most $p(|x|)$. \\
Let us define: \\
$ZPP = \{\lang \subseteq \AB^*: \text{ there exists an expected poly-time TM that decides } \lang\}$ \\
Prove that $ZPP = RP \cap coRP$.

Proof: \\
We need to show that: \\
1. $ZPP \subseteq RP \cap coRP$ \\
2. $ZPP \supseteq RP \cap coRP$ \\

\underline{$ZPP \subseteq RP \cap coRP$:} \\
Let $\lang \in ZPP$, so there exists an expected poly-time TM $M$ with poly-time $p$, that decides $\lang$. \\
We will show that $\lang \in RP \cap coRP$, by showing that $\lang \in RP \wedge \lang \in coRP$:

\underline{$\lang \in RP$:} \\
We shall define probabilistic TM $M_{RP}$ for $\lang$.  \\
$M_{RP}$ on input $x$:
\begin{enumerate}[1., itemsep=5pt]
    \item Run $M$ on $x$ for $2p(|x|)$ steps.
    \item If it stops, answer as $M(x)$ answers.
    \item Reject.
\end{enumerate}
We denote by $T_{M,x}$ (random variable) the runtime of $M$ on input $x$ until it stops.

So we get $\forall x \in \AB^*$: \\
If $x \in \lang$ \\
$\Longrightarrow M$ accepts $x$ in expected poly-time $p(|x|)$ \\
$\Longrightarrow M_{RP}$ rejects $x$ only if $T_{M,x} > 2p(|x|)$ \\
$\Longrightarrow M_{RP}$ rejects $x$ with probability (Markov's Inequelity):
\[ P(T_{M,x} \geq 2p(|x|)) \leq E[T_{M,x}] / 2p(|x|) = p(|x|) / 2p(|x|) = 1/2 \]
$\Longrightarrow M_{RP}$ accepts $x$ with probability $\geq 1/2$

If $x \notin \lang$ \\
$\Longrightarrow M$ rejects $x$ \\
$\Longrightarrow M_{RP}$ rejects $x$ whether $M(x)$ will stop or not \\

Notice that the TM's runtime is polynomial $= O(2p(|x|)) = O(p(|x|))$ \\
Therefore $\lang \in RP$. \\

\underline{$\lang \in coRP$:} \\
We shall define probabilistic TM $M_{coRP}$ for $\lang$
$M_{coRP}$ on input $x$:
\begin{enumerate}[1., itemsep=5pt]
    \item Run $M$ on $x$ for $2p(|x|)$ steps.
    \item If it stops, answer as $M(x)$ answers.
    \item Accept.
\end{enumerate}
We denote by $T_{M,x}$ (random variable) the runtime of $M$ on input $x$ until it stops.

\pagebreak
So we get $\forall x \in \AB^*$: \\
If $x \in \lang$ \\
$\Longrightarrow M$ accepts $x$ \\
$\Longrightarrow M_{coRP}$ accepts $x$ whether $M(x)$ will stop or not

If $x \notin \lang$ \\
$\Longrightarrow M$ rejects $x$ in expected poly-time $p(|x|)$ \\
$\Longrightarrow M_{coRP}$ accepts $x$ only if $T_{M,x} > 2p(|x|)$ \\
$\Longrightarrow M_{coRP}$ accepts $x$ with probability (Markov's Inequelity):
\[ P(T_{M,x} \geq 2p(|x|)) \leq E[T_{M,x}] / 2p(|x|) = p(|x|) / 2p(|x|) = 1/2 \]
$\Longrightarrow M_{coRP}$ accepts $x$ with probability $\leq 1/2$ \\

Notice that the TM's runtime is polynomial $= O(2p(|x|)) = O(p(|x|))$ \\
Therefore $\lang \in coRP$. \\

Hence $\lang \in RP \cap coRP \Rightarrow ZPP \subseteq RP \cap coRP$. \\

\underline{$ZPP \supseteq RP \cap coRP$:} \\
Let $\lang \in RP \cap coRP$, so $\lang \in RP \wedge \lang \in coRP$. Therefore there exists
probabilistic TM $M_{RP}, M_{coRP}$ such that: \\
- If $x \in    \lang: M_{RP}$ accepts $x$ with probability $\geq 1/2$, $M_{coRP}$ always accepts $x$,  \\
- If $x \notin \lang: M_{RP}$ always rejects $x$, $M_{coRP}$ accepts $x$ with probability $\leq 1/2$ \\
(*) Therefore if $M_{RP}$ accepts $x$, then definitely $x \in \lang$
and if $M_{coRP}$ rejects $x$, then definitely $x \notin \lang$. \\

We define TM $M$ for language $\lang$: \\
$M$ on input $x$:
\begin{enumerate}[1., itemsep=5pt]
    \item Run $M_{RP}$ on $x$ with new random string $r$, if it accepts - accept.
    \item Run $M_{coRP}$ on $x$ with new random string $r$, if it rejects - reject.
    \item Return to step 1.
\end{enumerate}

Notice that $M$'s answer is always correct, since we run both TMs until we get an answer according to (*).
Since the probability of error for $M_{RP}, M_{coRP}$ in each case is $1/2$,
each of them is expected to run twice, since their runtime is polynomial we get that
the algorithm's runtime is expected poly-time.

Hence $\lang \in ZPP \Rightarrow ZPP \supseteq RP \cap coRP$. \\
so we get that $ZPP = RP \cap coRP$. As required.
