Let us define $Prefix(\lang) = \{x : \exists y \text{ such that } xy \in \lang\}$

\begin{enumerate}[i.]
    \item $\REcl$ is closed under Prefix.

          The claim is true. \\

          Proof: \\
          Let there be $\lang \in \REcl$, we will show that $Prefix(\lang) \in \REcl$. \\
          $\lang \in \REcl$ so there is TM $M$ that accepts $\lang$. \\
          We shall build a non-deterministic TM $N$ that accepts $Prefix(\lang)$:

          $N \text{ on input } x$: \\
          1. Order $\AB^*$ in a lexicographic order. \\
          2. For each word $y$ in that order, run $M$ on $w=xy$ in parallel. \\
          3. Accept iff $M$ accepts for some word $w=xy$. \\

          Note - instead of using a non-deterministic TM, we can run $M$ on each of \\
          the words in 'parallel' by running each time on an increasing number of \\
          words for an increasing number of steps, just like we did in the lecture and recitation. \\

          So we get: \\
          If $x \in Prefix(\lang)$ then: \\
          $\exists y \in \AB^*: w=xy \in \lang \rightarrow $ in one of the computational
          paths for input $x$, $N$ will choose $y$ for input $x$ and $M$ would accept $w=xy$. \\
          $\rightarrow N$ accepts. \\

          If $x \notin Prefix(\lang)$ then: \\
          $\nexists y \in \AB^*: w=xy \in \lang \rightarrow $ there is no computational
          path for input $x$, in which $N$ will choose $y$ such that $w=xy \in \lang$,
          so $M$ would reject or be stuck in a loop for every $w=xy$. \\
          $\rightarrow N$ rejects or stuck in a loop. \\

          Indeed we get that $N$ accepts $Prefix(\lang)$. \\
          So we get that $\REcl$ is closed under Prefix, as required. \\

    \item $\Rcl$ is closed under Prefix.

          The claim is false. \\

          Proof: \\
          Lets assume that $\Rcl$ is closed under Prefix. We saw that $HALT \in \REcl \backslash \Rcl$
          so there is TM $M_{HALT}$ that accepts it. \\
          Observe the following language (over $\AB_1 = \AB \cup \{\#, 0\} \text{ assuming w.l.o.g. } \AB \cap \{\#\} = \emptyset$):
          \[
              \lang = \{\langle M, w \rangle \#0^k : M_{HALT} \text{ accepts } \langle M, w \rangle \text{ in k steps}\}
          \]
          Notice that $\lang \in \Rcl$, since we can build TM $M$ that decides it:

          $M \text{ on input } x$: \\
          1. If $x$ is not in the format of $\langle M, w \rangle \#0^k$ for some $k \in \nat$ - reject. \\
          2. If $\langle M, w \rangle$ is not a valid encoding - reject. \\
          3. Count the number of 0's after \#, denote the number as $k$. \\
          4. Run $M_{HALT}$ on $\langle M, w \rangle$ for $k$ steps. \\
          5. Accept iff $M_{HALT}$ accepts. \\

          So we get: \\
          If $x \in \lang$ then: \\
          $x$ is of the required format and $\langle M, w \rangle$ is a valid encoding. if the number of 0's after \# is $k$, then
          $M_{HALT} \text{ accepts } \langle M, w \rangle \text{ in k steps}$.  \\
          $\rightarrow M$ accepts. \\

          If $x \notin \lang$ then: \\
          $x$ is not of the required format or $\langle M, w \rangle$ is not a valid encoding or
          if the number of 0's after \# is $k$, then $M_{HALT}$ on $\langle M, w \rangle$ would not accept after $k$ steps: \\
          If $x$ is not of the required format or $\langle M, w \rangle$ is not a valid encoding - we reject. \\
          If the number of 0's after \# is $k$, then $M_{HALT}$ on $\langle M, w \rangle$ would not accept after $k$ steps,
          in that case we also reject. \\
          $\rightarrow M$ rejects. \\

          We got that $M$ decides $\lang$ so $\lang \in \Rcl$.\\
          we assumed that $\Rcl$ is closed under Prefix, so $Prefix(\lang) \in \Rcl$.
          Therefore there is TM $M'$ that decides $Prefix(\lang)$.
          But, now we get that we can construct TM $M''$ that decides HALT: \\

          $M'' \text{ on input } \langle M, w \rangle$: \\
          1. If $\langle M, w \rangle$ is not a valid encoding - reject. \\
          2. Run $M'$ on $\langle M, w \rangle \#$. \\
          3. Accept iff $M'$ accepts. \\

          So we get: \\
          If $\langle M, w \rangle \in HALT$ then: \\
          $\langle M, w \rangle$ is a valid encoding and $M_{HALT}$ on
          input $x$ stops after $k$ steps. \\
          $\rightarrow \langle M, w \rangle \#0^k \in \lang$ \\
          $\rightarrow \langle M, w \rangle \# \in Prefix(\lang)$. \\
          $\rightarrow M'$ accepts. \\
          $\rightarrow M''$ accepts. \\

          If $\langle M, w \rangle \notin HALT$ then: \\
          $\langle M, w \rangle$ is not a valid encoding or $M_{HALT}$ on
          Input $\langle M, w \rangle$ doesn't halt. \\
          If $\langle M, w \rangle$ is not a valid encoding - we reject. \\
          If $M_{HALT}$ on input $\langle M, w \rangle$ doesn't halt, then there is no $k$
          such that $\langle M, w \rangle \#0^k \in \lang$.  \\
          $\rightarrow \langle M, w \rangle \# \notin Prefix$. \\
          $\rightarrow M'$ rejects. \\
          $\rightarrow M''$ rejects. \\

          So $HALT \in \Rcl$.
          We got $HALT \in \Rcl$ in contradiction with $HALT \notin \Rcl$. \\
          Hence we get that $\Rcl$ is not closed under Prefix, as required. \\

\end{enumerate}