$\NPcl$ is closed under Kleene Star. \\

Proof: \\
Let there be $\lang \in \NPcl$, we will show that $\lang^* \in \NPcl$. \\
$\lang \in \NPcl$ so there is a non-deterministic TM $N$ that decides $\lang$ in polynomial time $p$. \\
We shall build a non-deterministic TM $N'$ that decides $\lang^*$ in a polynomial time of its input's length:

$N'$ on input $x$:
\begin{enumerate}[1., itemsep=5pt]

    \item Choose an arbitrary split of $x$ to parts.

    \item Run $N$ on each of the parts (one after the other).

    \item Accept iff $N$ accepts all parts.

\end{enumerate}

So we get: \\
If $x \in \lang^*$ then: \\
$\exists x_1,...,x_n \in \lang: x=x_1...x_n \rightarrow $ in one of the computational
paths for input $x$, $N'$ will choose the $x=x_1...x_n$ split for $x$ and $N$ would accepts all of its parts
(since $\forall 1 \leq i \leq n: x_i \in \lang$). \\
$\rightarrow N'$ accepts. \\

If $x \notin \lang^*$ then: \\
$\nexists x_1,...,x_n \in \lang: x=x_1...x_n \rightarrow $ there is no computational
path for input $x$, in which $N'$ will choose a split such that $N$ would accepts all of its parts.
Because $N$ decides $\lang$, we will get that $N$ will reject at least one of the parts in
each of the arbitrary splits and accept the others and wouldn't be stuck in a loop. \\
$\rightarrow N'$ rejects. \\

Indeed, we get that $N'$ decides $\lang^*$. \\
And its runtime on input $x$ is: \\
- For step (1): $O(|x|)$ \\
- For step (2): $p(|x|) \cdot$(number of parts of $x$) = $p(|x|) \cdot O(|x|)$ \\
- For step (3): $O(|x|)$

Thus, the total runtime of $N'$ on input $x$ is polynomial in $|x|$.

So we get that $\NPcl$ is closed under Kleene Star, as required. \\

