$\Pcl$ is closed under Kleene Star. \\

Proof: \\

Let there be $\lang \in \Pcl$, we will show that $\lang^* \in \Pcl$. \\
$\lang \in \Pcl$ so there is a deterministic TM $M$ that decides $\lang$ in polynomial time $p$. \\
We shall build a deterministic TM $M'$ (using dynamic programming) that decides $\lang^*$ in a polynomial time of its input's length.

First note that $w \in \lang^*$ iff one of the following cases holds:

\begin{enumerate}[(1), itemsep=5pt]
    \item $w = \empw$
    \item $w \in \lang$
    \item $\exists x,y \in \lang^* \backslash \{\empw\}: w=xy$
\end{enumerate}

We denote: $w_{i,j} = w_i...w_j$ \\
Now we will define $M'$ according to the cases above working bottom-up: \\
$M'$ on input $w=w_{1,n}=w_1...w_n$:

\begin{enumerate}[1., itemsep=10pt]

    \item \bd{If $w = \empw$ - accept.} (Check Case (1))

    \item \bd{Initialize array $A$ of size $n^2$: $A[i, j] = 0, \forall 1 \leq i \leq j \leq n$} \\
          (we will only use $(n^2+n)/2$ cells of $A$ - its diagonal and the cells above it, \\
          assuming indices start from 1 and end at $n$)


    \item \bd{For $i \leftarrow 1$ to $n$:}                                                  (Check all substrings of length 1)
    \item \qquad  \bd{$A[i, i] = 1$ if $M$ accepts $w_i$}                                    (= $w_i \in \lang$) (Check Case (2))

    \item \bd{For $length \leftarrow 2$ to $n$: }                                            (Go over the possible lengths from smallest to largest)
    \item \qquad  \bd{For $i \leftarrow 1$ to $n - length + 1$:}                             (Go over the relevent starting indices)
    \item \qquad \qquad  \bd{Let $j = i + length - 1$ }                                      (Infer end of substring from $i$ and $length$)

    \item \qquad \qquad  \bd{$A[i, j] = 1$ if $M$ accepts $w_{i,j}$ (= $w_{i,j} \in \lang$)} (Check Case (2))

    \item \qquad \qquad  \bd{For $k \leftarrow i$ to $j-1$:}
    \item \qquad \qquad \qquad  \bd{$A[i, j] = 1$ if $A[i, k] = 1$ and $A[k + 1, j] = 1$}    (= $w_{i,k}, w_{k+1,j} \in \lang^*$, Case (3))


    \item  \bd{If $A[1, n] = 1$ - accept, otherwise reject.}

\end{enumerate}

The algorithm checks whether $w \in \lang^*$ by checking if its substrings are in $\lang^*$ -
it starts from the shortest substrings (length 1) and incrementaly increases the length
of the substrings while using the result for shorter strings to get the answer. \\

So we get: \\
If $w \in \lang^*$ \\
$\Rightarrow w = \empw$ or $w \in \lang$ or $\exists x,y \in \lang^* \backslash \{\empw\}: w=xy$ \\
If $w = \empw$  $\Rightarrow $ from step 1 - $M'$ accepts. \\
If $w \in \lang$  $\Rightarrow $ from step 8 - $M'$ accepts. \\
If $\exists x,y \in \lang^* \backslash \{\empw\}: w=xy$  $\Rightarrow $ from step 10 - $M'$ accepts. \\
$\Rightarrow M'$ accepts. \\

If $w \notin \lang^*$ \\
$\Rightarrow w \neq \empw$ and $w \notin \lang$ and $\nexists x,y \in \lang^* \backslash \{\empw\}: w=xy$ \\
$\Rightarrow M'$ rejects. \\

Indeed, we get that $M'$ decides $\lang^*$. \\
And its runtime on input $w$ (where $|w|=n$) is: \\
- For step  (1):    $O(1)$                            \\
- For step  (2):    $O(n^2)$                          \\
- For steps (3-4):  $O(n \cdot p(n))$                 \\
- For steps (5-10): $O(n^2 \cdot p(n) + n^2 \cdot n)$ \\
- For step  (11):   $O(1)$                            \\

Thus, the total runtime of $M'$ on input $x$ is polynomial in $|x|=n$, so $\lang^* \in \Pcl$. \\
So we get that $\Pcl$ is closed under Kleene Star, as required. \\

