Prove that if $\Pcl = \NPcl$, then there exists a polynomial-time TM that given a CNF formula \\
$\phi$ outputs a satisfying assignment for $\phi$ or indicates one does not exists. \\

Proof: \\
First notice that $CNFSAT = \{\phi: \phi \text{ is a satisfiable CNF formula}\} \in \NPcl$,
since we can build a polynomial verifier $V$ for it:

$V$ for input $(\langle \phi \rangle, w)$:
\begin{enumerate}[1., itemsep=5pt]
    \item Verify that $(\langle \phi \rangle$ is an encoding of a valid CNF formula, if it's not - reject.

    \item Verify that $w$ is a possible assignment to the variables in $\phi$, if it's not - reject.

    \item Assign values to the variables in $\phi$ according to $w$, if the formula is satisfied - accept, otherwise reject.

\end{enumerate}

Indeed: \\
If $\langle \phi \rangle \in CNFSAT$ \\
$\Rightarrow \langle \phi \rangle$ is a valid encoding of a CNF formula
and there exists an assignment to its variables $w \in \AB^*$ such that $\phi$ is satisfied. \\
$\Rightarrow $ There exists $w \in \AB^*$ such that $V$ accepts $(\langle \phi \rangle, w)$. \\

If $\langle \phi \rangle \notin CNFSAT$ \\
$\Rightarrow \langle \phi \rangle$ is not a valid encoding of a CNF formula
or there doesn't exist an assignment to its variables $w \in \AB^*$ such that $\phi$ is satisfied. \\
If $\langle \phi \rangle$ is not a valid encoding of a CNF formula $\Rightarrow V$ rejects. \\
If there doesn't exist an assignment to $\phi$'s variables $w \in \AB^*$ such that $\phi$ is satisfied \\
$\Rightarrow V$ rejects $(\langle \phi \rangle, w)$ for every $w \in \AB^*$.

Also $V$'s runtime on input $(\langle \phi \rangle, w)$ (where $|(\langle \phi \rangle, w)|=n$) is: \\
- For step (1): $O(n)$ \\
- For step (2): $O(n)$ \\
- For step (3): $O(n)$ \\
Thus, the total runtime of $V$ on input  $(\langle \phi \rangle, w)$ is polynomial in $|(\langle \phi \rangle, w)|=n$, so $CNFSAT \in \NPcl$. \\
But it is given that $\Pcl = \NPcl$, so $CNFSAT \in \Pcl$.
Therefore there is a deterministic TM $M$ that decides $CNFSAT$ in polynomial time $p$. \\

We shall build a deterministic TM $M'$ that given a CNF formula $\phi$ outputs a satisfying
assignment for $\phi$ or indicates one does not exists in a polynomial-time. \\
First we set $M'$'s $\AB_{M'}$ to be $\AB_{M'}=\AB_{M} \cup \{\otimes\}$ assuming w.l.o.g.
$\AB_{M} \cap \{\otimes\} = \emptyset$ (to indicate if a satisfying assignment doesn't exist)

\pagebreak

Now we define $M'$: \\
$M'$ on input $\langle \phi \rangle$:
\begin{enumerate}[1., itemsep=5pt]

    \item Run $M$ on $\langle \phi \rangle$, if it rejects - output $\otimes$ and reject.

    \item Extract the variables of $\phi$ from $\langle \phi \rangle$, let us denote them as $x_1,...,x_n$.

    \item For $i \leftarrow 1$ to $n$:
    \item \qquad Add $x_i = 1$ to current assignment $x_1,...,x_{i-1}$
    \item \qquad Calculate the new CNF formula $\langle \phi_i \rangle$ with current assignment $x_1,...,x_i$
    \item \qquad Run $M$ on $\langle \phi_i \rangle$, if it rejects - assign $x_i = 0$ instead of $x_i = 1$ in the current assignment.

    \item Output the current assignment $x_1,...,x_n$ and accept.

\end{enumerate}


Step (1) verifies that $\langle \phi \rangle$ is a valid CNF formula and is satisfiable, if its not - it indicates that a satisfying
assignment for $\phi$ does not exists and rejects. If it is a valid CNF formula and is satisfiable - we continue to the next steps.

Step (2) extracts the variables from the formula.

Steps (3-6) go over the variables one by one, and try assigning values to the variables - it assigns a value to a variable and makes
sure that the formula is still satisfiable. If it is not, it means that we need to assign the opposite value to the variable
(since we know that the formula is satisfiable). At the end the variables will hold the satisfying assignment.

Step (7) outputs the satisfying assignment and accepts.

We check that the relevent formula is satisfiable at each step, by running $M$ with the formula's encoding as its input.

$M'$'s runtime on input $\langle \phi \rangle$ (where $|\langle \phi \rangle|=n$) is: \\
- For step  (1):     $O(p(n))$                         \\
- For step  (2):     $O(n)$                            \\
- For steps (3-6):   $O(n \cdot (n+p(n)))$             \\
- For step (7):      $O(n)$                            \\

Hence $M'$ on a CNF formula $\phi$, outputs a satisfying assignment for $\phi$
or indicates one does not exists in a polynomial-time. As required. \\

{
\color{red}
\transparent{0.5}
}