Input: a 3CNF formula $\phi$ such that literals in each clause correspond
to three distinct variables (e.g., $x_1 \vee x_2 \vee \neg x_3$ but not $x_1 \vee x_2 \vee \neg x_2$). \\
Question: does there exist an assignment that satisfies $\phi$?

We need to show that: \\
$\lang = \{\phi \in 3SAT: \text{ literals in each clause of $\phi$ correspond
        to three distinct variables }\} \in \NPCcl$ \\

Proof: \\
We need to show that: \\
1. $\lang \in \NPcl$ \\
2. $\forall \lang' \in \NPcl: \lang' \leq_p \lang$ by showing that $3SAT \leq_p \lang$ (we can do this since $3SAT \in \NPCcl$) \\

First we show that $\lang \in \NPcl$, by building a polynomial verifier $V$ for it. \\
$V$ for input $(\langle G \rangle, w)$:
\begin{enumerate}[1., itemsep=5pt]
    \item Verify that $\langle \phi \rangle$ is a valid encoding of a 3CNF formula with three distinct variables in each clause, if it is not - reject.

    \item Verify that $w$ is a possible assignment to the variables in $\phi$, if it's not - reject.

    \item Assign values to the variables in $\phi$ according to $w$, if the formula is satisfied - accept, otherwise reject.

\end{enumerate}

So we get: \\
If $\langle \phi \rangle \in \lang$ \\
$\Rightarrow \langle \phi \rangle$ is a valid encoding of a 3CNF formula with three distinct variables in each clause
and there exists an assignment to its variables $w \in \AB^*$ such that $\phi$ is satisfied. \\
$\Rightarrow $ There exists $w \in \AB^*$ such that $V$ accepts $(\langle \phi \rangle, w)$. \\

If $\langle \phi \rangle \notin \lang$ \\
$\Rightarrow \langle \phi \rangle$ is not a valid encoding of a 3CNF formula with three distinct variables in each clause
or there doesn't exist an assignment to its variables $w \in \AB^*$ such that $\phi$ is satisfied. \\
If $\langle \phi \rangle$ is not a valid encoding of a 3CNF formula with three distinct variables in each clause $\Rightarrow V$ rejects. \\
If there doesn't exist an assignment to $\phi$'s variables $w \in \AB^*$ such that $\phi$ is satisfied \\
$\Rightarrow V$ rejects $(\langle \phi \rangle, w)$ for every $w \in \AB^*$.

Also $V$'s runtime on input $(\langle \phi \rangle, w)$ (where $|\langle \phi \rangle|=n$) is: \\
- For step (1): $O(n)$ \\
- For step (2): $O(n)$ \\
- For step (3): $O(n)$ \\
Thus, the total runtime of $V$ on input  $(\langle \phi \rangle, w)$ is polynomial in $|\langle \phi \rangle|=n$, so \underline{$\lang \in \NPcl$}. \\

\pagebreak

Now, we will show that there is a polynomial reduction from $3SAT$ to $\lang$: \\
First we show reduction for a single clause, we define the following function: \\
$g: \AB^* \rightarrow \AB^*$: \\

$C = \emptyset$ ($C$ is an empty clause, not satisfiable) \\
$\Rightarrow g(C) = (x \vee y \vee z) \wedge (x \vee y \vee \neg z) \wedge (x \vee \neg y \vee z) \wedge (x \vee \neg y \vee \neg z)
    \wedge (\neg x \vee y \vee z) \wedge (\neg x \vee y \vee \neg z) \wedge (\neg x \vee \neg y \vee z) \wedge (\neg x \vee \neg y \vee \neg z)$,
where $x, y, z$ are new variables. \\

$C = (x) = (x \vee x \vee x)$ \\
$\Rightarrow g(C) = (x \vee y \vee z) \wedge (x \vee y \vee \neg z) \wedge(x \vee \neg y \vee z) \wedge(x \vee \neg y \vee \neg z)$, where $y, z$ are new variables. \\

$C = (x \vee y) = (x \vee y \vee x) = (x \vee y \vee y) $ \\
$\Rightarrow g(C) = (x \vee y \vee z) \wedge (x \vee y \vee \neg z)$, where $z$ is a new variable. \\

$C = (x \vee y \vee z)$ \\
$\Rightarrow g(C) = (x \vee y \vee z) = C$. \\

for every other case, we define $g(C) = 0$. \\
Notice that $g$ doesn't change the logic of the formula, so $C$ is satisfiable iff $g(C)$ is satisfiable
with same assignment of the existing variables and an arbitrary assignment of the new variables. \\
Also, notice that $g$ is computable in a polynomial time in $|C|$. \\

Now, we define the reduction from a whole formula in $3SAT$ to a whole formula in $\lang$: \\
$f: \AB^* \rightarrow \AB^*$: \\
$
    f(\langle \phi \rangle) =
    \begin{cases}
        \langle \phi  \rangle,                                         & \langle \phi \rangle \text{ is not a valid encoding } \\
        \langle g(C_1) \wedge g(C_2) \wedge ... \wedge g(C_n) \rangle, & else (\phi = C_1 \wedge C_2 \wedge ... \wedge C_n)    \\
    \end{cases}
$

Where $C_1, C_2,...,C_n$ are the clauses of $\phi$. \\
Notice that $f$ is computable in polynomial time in $|\langle \phi \rangle|$, since we just check
if the input's encoding is valid and if it is - we apply $g$ (which is computable in a polynomial time) to each of the $n$ clauses of $\phi$.

Also $\forall x = \langle \phi \rangle \in \AB^*$:

If $x = \langle \phi \rangle \in 3SAT$ \\
$\Rightarrow \phi = C_1 \wedge C_2 \wedge ... \wedge C_n$ is a valid 3CNF formula that is satisfiable \\
$\Rightarrow f(\langle \phi \rangle) = \langle g(C_1) \wedge g(C_2) \wedge ... \wedge g(C_n) \rangle$,
is satisfiable since each clause $C$ is satisfiable iff $g(C)$ is satisfiable with same assignment of the
existing variables and an arbitrary assignment of the new variables. Meaning that the satisfying assignment
for $\phi$ is same satisfying assignment for $f(\langle \phi \rangle)$ (with the addition of an arbitrary
assignment to the new variables). \\
Also from the definition of $g$ each clause $g(C)$ has 3 distinct variables. \\
$\Rightarrow f(\langle \phi \rangle) \in \lang$ \\

If $x = \langle \phi \rangle \notin 3SAT$ \\
$\Rightarrow \langle  \phi \rangle$ is not valid encoding of a 3CNF formula or it is, but is not satisfiable \\

If $\langle \phi \rangle$ is not valid encoding of a 3CNF formula \\
$\Rightarrow f(\langle \phi \rangle) = \langle \phi \rangle \notin \lang$ \\

If $\langle \phi = C_1 \wedge C_2 \wedge ... \wedge C_n \rangle$ is a valid encoding of a 3CNF formula but is not satisfiable \\
$\Rightarrow f(\langle \phi \rangle) = \langle g(C_1) \wedge g(C_2) \wedge ... \wedge g(C_n) \rangle$,
is not satisfiable since each clause $C$ is satisfiable iff $g(C)$ is satisfiable with same assignment of the
existing variables and an arbitrary assignment of the new variables. Meaning that since there is no satisfying assignment
for $\phi$ then there is no satisfying assignment for $f(\langle \phi \rangle)$  \\
$\Rightarrow f(\langle \phi \rangle) \notin \lang$ \\

So we get \underline{$3SAT \leq_p \lang$}. \\
In conclusion, $\lang \in \NPCcl$. As required.

